%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}  % Font Latin Modern hỗ trợ tiếng Anh tốt
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}
\setlength{\footskip}{4pt}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[1]{  
\item\small{
    \textbf{#1}\vspace{-2pt}}
  }
\definecolor{myblue}{RGB}{0, 102, 204}
\definecolor{mycolor}{RGB}{255, 64, 64}
\newcommand{\nhref}[2]{\textcolor{mycolor}{\href{#1}{#2}}}
  

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
  % Avatar bên trái (giảm size một chút để thanh thoát hơn)
  \begin{minipage}{0.25\textwidth}
    
  \end{minipage} &
  % Thông tin bên phải, căn phải sát mép
  \begin{minipage}{0.70\textwidth}
    \raggedleft
    \textbf{{\Huge Chau Duong Phat Tien}} \\ \vspace{2pt}
    {\color{myblue} \textbf{\large BACKEND / FULLSTACK DEVELOPER}} \\ \vspace{6pt} \vspace{4pt}
    \small
    Email: \href{mailto:chauduongphattien2201@gmail.com}{chauduongphattien2201@gmail.com} \\
    Github: \href{https://github.com/ChauTienPro10}{github.com/ChauTienPro10} \\
    Linkedin: \href{https://www.linkedin.com/in/chau-duong-phat-tien-251608303/?lipi=urn%3Ali%3Apage%3Ad_flagship3_profile_view_base_contact_details%3BUGlf8MV3SOmmxJJGBqYEOQ%3D%3D}{chauduongphattien} \\
    Mobile: 0812788212 \\
    ZALO: 0812788212 \\
  \end{minipage}
\end{tabular*}


\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {Ho Chi Minh University of Technology and Education (HCMUTE)}{Ho Chi Minh City, Vietnam}
  {Major: Software Engineering} {2021 -- 2026}
\resumeSubHeadingListEnd

\section{SUMMARY}
\resumeSubHeadingListStart
    \resumeItem{Professional experience}{\newline * Full-Stack Engineer with 2+ years of experience, specializing in Java backend along with modern frontend and mobile frameworks including Angular, ReactJS, and React Native. \newline * Full-Stack developer at FPT IS(Java SpringBoot, Angular, Microk8s, MongoDB). \newline * Progressed from Intern to Fresher, and subsequently served as a Backend Developer at EVERRISE.}

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
       
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java (Core, OOP, Multithreading), TypeScript, JavaScript, C\#} \\
     \textbf{Backend Frameworks}{: Spring Framework (Boot, MVC, Security, Data JPA)} \\
     \textbf{Databases \& Caching}{: MySQL, PostgreSQL, SQL Server, MongoDB (Query Optimization, Indexing)} \\
     \textbf{Frontend \& Mobile}{: ReactJS, Angular, React Native} \\
     \textbf{DevOps, Cloud \& Architecture}{: Microservices, Docker, Kubernetes, Jenkins, GCP, Linux} \\
     \textbf{Tools \& Version Control}{: Git, SVN}
    }}
\end{itemize}
  
\section{Work Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {FPT Information System (FPT IS)}{03/2025 -- Present}
      {Fullstack Developer}{Ho Chi Minh City, Vietnam}
      \resumeItemListStart
        \item \textbf{Project: HIE System (Health Information Exchange) -- Hoan My Hospital}
        \begin{itemize}
            \item Developed a comprehensive healthcare platform serving multiple hospitals, including a \textbf{Mobile App} (React Native) for patients, a \textbf{Web Admin} (Angular) for hospital staff, a \textbf{Self-service Kiosk} for automated check-in, and a \textbf{HIS Integration Service} connecting with legacy hospital systems.
            \item Designed and optimized \textbf{MongoDB} collections for patient records, booking management, and carebook data; wrote \textbf{SQL Server} queries for bidirectional sync with the HIS Core system via Debezium CDC and Kafka.
            \item Built backend microservices (Spring Boot) handling appointment booking, patient profiles, kiosk device monitoring (heartbeat, online/offline status), and real-time notifications via SSE/WebSocket.
            \item Developed the \textbf{Kiosk Admin Dashboard}: real-time device status monitoring, activity logs, and alert management for all kiosk terminals across hospital branches.
            \item Containerized and deployed the system using \textbf{Docker} and \textbf{MicroK8s}; maintained 20+ independent microservices with CI/CD pipelines.
        \end{itemize}

         \item \textbf{Project: Self-service Kiosk Application for  Binh Thanh General Hospital}
        \begin{itemize}
            \item \textit{}Maintained and supported the self-service kiosk app, ensuring smooth patient registration and queue ticket issuance.
        \end{itemize}

        \item \textbf{Project: Pham Ngoc Thach University Clinic}
        \begin{itemize}
            \item \textit{HOSPITAL INFORMATION SYSTEM}
            \item \textit{Responsibilities}: 
            \begin{itemize}
                \item Contributed to the core system development, focusing on modules for clinical workflows, hospital management, and patient administration.
                \item Designed and integrated standardized medical report templates and test result sheets in compliance with healthcare standards.
                \item Developed API integrations with the National Pharmacy Database for automated drug data synchronization.
            \end{itemize}
        \end{itemize}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
    {EVERRISE}{08/2024 - 03/2025}
    {Backend Developer}{}
    \begin{itemize}
        \item \textbf{Project: ETL-Harbest} -- An ETL system processing advertising data from TikTok, X, Google Ads for Japanese clients. Includes WebAPI for OAuth2-based auth and batch processes for data extraction/export.
        \item Developed Java-based batch jobs to fetch and transform ad data across platforms.
        \item Enhanced Web API system using OAuth2 authentication.
        \item Diagnosed and resolved real-time system and integration issues.
        \item Worked closely with AWS services like S3 (object storage) and RDS (relational DB).
    \end{itemize}
\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------

\section{Personal Projects}
\resumeSubHeadingListStart
    \resumeSubheading
      {E-Banking Microservices Platform}{2025 -- 2026}
      {Personal Project -- Full-Stack Developer}{}
      \resumeItemListStart
        \item Built a full-featured digital banking platform with \textbf{10 independent microservices} using Java 17, Spring Boot 3.x, Spring Cloud, and React 19 (TypeScript).
        \item Implemented \textbf{gRPC} for synchronous inter-service communication (auth, user, email) and \textbf{Apache Kafka} for async event streaming (transactions, notifications).
        \item Integrated \textbf{eKYC} via FPT AI SDK (OCR, Liveness Detection, Face Matching) and \textbf{AI Chatbot} using Google Gemini API with function calling.
        \item Built \textbf{real-time features}: WebSocket/STOMP for live chat and transaction updates; \textbf{multi-channel notifications} via Firebase Cloud Messaging and SMTP email (Thymeleaf templates).
        \item Secured the system with Spring Security, JWT (access + refresh tokens), BCrypt, and Redis-based session management.
        \item Containerized all services with \textbf{Docker Compose}; set up \textbf{Jenkins} CI/CD pipeline and \textbf{Prometheus + Grafana} monitoring.
        \item \textbf{Stack:} Java 17, Spring Boot, Spring Security, gRPC, Kafka, Redis, MySQL, React 19, TypeScript, TailwindCSS, Docker, Nginx, Eureka, Jenkins.
      \resumeItemListEnd

    \resumeSubheading
      {Online Judge -- Coding Practice Platform}{2026}
      {Personal Project -- Backend Developer}{}
      \resumeItemListStart
        \item Built an online code execution platform (similar to LeetCode) that allows users to write, compile, and run Java code with automated test case evaluation.
        \item Designed a \textbf{Docker-isolated execution engine}: user-submitted code is compiled and run inside a dedicated JDK container (\texttt{eclipse-temurin:21-jdk}), with automatic file cleanup after each execution -- ensuring security and isolation.
        \item Implemented \textbf{multi-threaded processing} (Java 21) to handle concurrent compile/run requests without blocking the main thread.
        \item Designed challenge management with \textbf{One-to-Many test case mapping} (MySQL, Spring Data JPA); supports per-test-case pass/fail reporting.
        \item Integrated \textbf{GitHub OAuth2} login via Spring Security OAuth2 Authorization Server.
        \item \textbf{Stack:} Java 21, Spring Boot 3, Spring Security, OAuth2, Docker, MySQL, JPA/Hibernate, MapStruct, Lombok.
      \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}